Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-03-31 DGMM2025/paper.tex
fixing compilation errors

\usepackage{changes}
\usepackage{amstex}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
    A cell complex is a decomposition of space into elementary units—vertices, edges, faces, and higher-dimensional counterparts—forming a combinatorial representation of geometric objects.
    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.

>>>>

\usepackage{changes}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{varwidth}
\setauthormarkup{}
\definechangesauthor[name=jo, color=magenta]{JO}
\definechangesauthor[name=rom, color=teal]{ROM}

@@

    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
